Where and How Do Models Fail? A Visual Exploration Tool for Analyzing and Interpreting Natural Language Inference Model

### 2018-03-21 paper/intro.tex

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and come up with hypothesis for
why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, recognize where the model fail is non-trivial. The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions that are essential to the model diagnostic process. Questions such as, how stable predictions are concerning small perturbation in the input, how these predictions arrive (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model. On the other hand, infer why the model fails is even more challenging. Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships between model inputs, critical internal mechanisms, as well the output predictions.

\begin{itemize}
    \item Study the classifier  vs. single instance evaluation
    \item Model agnostic vs. reveal intern states
    \item View model as invariant object vs. interrogate the model via partial/full updates
\end{itemize}

%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
To analyzing the
Many method has been

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:projTransition}
\vspace{-5mm}
\end{figure}

>>>>

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and come up with hypothesis for
why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, recognize where the model fail is non-trivial. The standard evaluation approach (i.e., the prediction accuracy on the test set) provides limited information and cannot answer many important questions that are essential to the model diagnostic process. Questions such as, how stable predictions are concerning small perturbation in the input, how these predictions arrive (i.e., the model may come up with the correct prediction by pickup unintended feature/alignment), and what are the often made mistakes, are all essential in systematic examination and evaluation of the model. On the other hand, infer why the model fails is even more challenging. Since neural network models are often referred to as black boxes, hypothesizing what happened in prediction process require the ability to peek inside the model and understand the intricate relationships among model inputs, critical internal mechanisms, as well the output predictions.

\begin{itemize}
    \item Study the classifier  vs. single instance evaluation
    \item Model agnostic vs. reveal internal states
    \item View model as invariant object vs. interrogate the model via partial/full updates
\end{itemize}

%%%%%%%%% accessing internal states are important %%%%%%%%%%%%
Several previous works~\cite{BilalJourablooYe2018} have dedicate to analyzing errors made in analyzing 
There has been a
To analyzing the
Many method has been

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{Language Inference Model Pipeline.}
\label{fig:projTransition}
\end{figure}
